Beyond the Numbers: Dissecting New York City's Leading Causes of Death Across Demographics

### 2024-03-17 paper/paper.qmd
updated paper

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages.
The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

# Additional data details

>>>>

Contrary to expectations, we find that in modelling the rank and magnitude of the leading cause of death for each ethnicity, utilizing posterior predictive checks, the Poisson distribution offers a better fit relative to the negative binomial distribution (Figure 3; Figure 4; Figure 5; Figure 6). This disproves our hypothesis in which we expected the negative binomial distribution to be a better fit. Results are robust to model cross-validation using LOO for each ethnicity. This is interesting in that a negative binomial distribution is often considered a better fit for estimating mortality, in large part due to overdispersion concerns, yet the Poisson model proved to be a better fit here given the data.

@@
